Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
added missing references.bib entries and updated total stencils found in intro
typo

\item We detail checking and inference algorithms for our
  specifications (\cref{sec:analysis}), derived from a
  denotational model for the specificaiton language
  (\cref{sec:semantics});

@@

\item We report on a quantitative study of stencil computations on a
  corpus of numerical Fortran program
  (\cref{sec:evaluation}), totalling one million lines of code. Our tool
  identifies and infers specifications for 35,000 stencil computations in the
  corpus. Approximately 10\% of the stencils we found are non-trivial,
  corresponding to code which is a possible source of errors. This validates
  our hypothesis that the majority of stencil computations have a regular
  shape, and validates the design of our language in its capability to capture
  many core patterns.

>>>>

\item We detail checking and inference algorithms for our
  specifications (\cref{sec:analysis}), derived from a
  denotational model for the specification language
  (\cref{sec:semantics});

@@

\item We report on a quantitative study of stencil computations on a
  corpus of numerical Fortran program
  (\cref{sec:evaluation}), totalling one million lines of code. Our tool
  identifies and infers specifications for 60,000 stencil computations in the
  corpus. Approximately 10\% of the stencils we found are non-trivial,
  corresponding to code which is a possible source of errors. This validates
  our hypothesis that the majority of stencil computations have a regular
  shape, and validates the design of our language in its capability to capture
  many core patterns.
